### 2016-07-13 Theorem1_FP.tex
cleaning up theorem 1

\begin{theorem}\label{thm1}
Fix $k, m, n > 0$ and define a hash-based filter as in section \ref{sec:hbf}, except the hash functions are defined by $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$, where $F \colon \calK \times U \sends [m]$ is a PRF. Let $Func(U,[m])$ be the set of all functions $\rho \colon \calK \times U \sends [m]$. Let $B_1, B_2$ be 2 adversaries attacking the PRF advantage of $F$, and $A$ be another adversary attacking the false positive game of hash-based filters with private hash functions, then 
\begin{equation}
\AdvFPSecHash{B,t}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + q \cdot \epsilon
\end{equation}
Note: Here, $q$ is the number of queries made to the $\QryOracle$ oracle and $\epsilon$ is the false positive error in the double hashing scheme given by Kirsch and Mitzenmacher. $\epsilon \rightarrow 0$, if $m/n \rightarrow \infty$ and/or $k \rightarrow \infty$ \cite{xxx}
\end{theorem}

\begin{proof}
The proof of the theorem will use a game playing argument as shown in Fig. \ref{fig:Game}. $\game{0}(A)$ exactly simulates $\ExpFPSecHash{B,t}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$. So,
\begin{equation}
\AdvFPSecHash{B,t}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
\end{equation}
 $\game{1}(A)$ and $\game{2}(A)$ attack 2 different filters with hash functions 
\begin{eqnarray*}
h_j(x) &=& ( F_{K_0}(x) + j\cdot \rho_2(x)) \bmod m\\
\mathrm{and,}\nudge h_j(x) &=& ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m 
\end{eqnarray*}

Here, $\rho_1$ and $\rho_2$ are random functions sampled from $Func(U,[m])$. Let adversaries $B_1, B_2$ simulate $\game{1}(A)$ and $\game{2}(A)$ respectively as shown in Fig. \ref{fig:BGame1}. When $b=1$, $B_1$ and $B_2$ exactly simulate $\game{0}(A)$
and $\game{1}(A)$. While, for $b=0$, $B_1$ wins, if $\game{1}(A)$ outputs 0, and  $B_2$ wins, if $\game{2}(A)$ returns 0.

@@

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.95}{
\hpagessd{.5}{.5}
{
\underline{\game{0}(A)}\\
$K_1, K_2 \getsr \calK$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$K_1 \getsr \calK$\\
$\rho \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = F_{K_1}(x)+i \cdot \rho(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{2}(A)}\\
$\rho_1,\rho_2 \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{$\game{3}(A)$}\\
$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
$count = 0$ \\%count will be used to keep track of queries made to $\QryOracle$\\
$win \gets false$\\
$\rho_1,\rho_2 \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
$count=count +1$\\
if $(count == \ell)$\\
$\nudge win = true$\\
$\nudge \mathrm{Ret} \nudge \Qry^{\HashOracle}(M,\tau,x)$\\
else \\
$\nudge \mathrm{Ret}\nudge 0$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\caption{Theorem \ref{thm1}:Game playing argument}\label{fig:Game}
\end{figure}

%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\begin{figure}
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\experimentv{Adversary \nudge B_1^{\calO}:}$\\
$K_1 \getsr \calK $\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
When $A$ halts with output $\calX^{'}$: \\
if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
}
{
$\experimentv{Adversary \nudge B_2^{\calO}:}$\\
%$d \getsr \bits $\\
$\rho_2 \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
When $A$ halts with output $\calX^{'}$: \\
if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
%if $d=0$\\
$\mathrm{Ret} \nudge \calO(x) + i\cdot \rho_2(x)$, for $i\in[1,k]$
}
}
\caption{Theorem \ref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\end{figure}

@@

%\caption{Adversary $A^{'}$ simulating $\game{3}(A)$} \label{AGame3}
\begin{figure}
\centering
\fpage{0.4}{
$\experimentv{Adversary \nudge A^{{'}\HashOracle}:}$\\
$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
$count = 0$\\
$\rho_1,\rho_2 \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge count = count + 1$\\
\nudge if $count == \ell$\\
$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,\tau,x)$\\
\nudge else\\
$\nudge$ $\nudge r = 0$\\
\nudge Ret $r$\\
When $A$ halts with output $\calX^{'}$\\
\nudge if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
\nudge\nudge Ret 0\\
\nudge if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
\caption{Theorem \ref{thm1}:Adversary $A^{'}$ simulating $\game{3}(A)$} \label{AGame3}
\end{figure}

>>>>

\heading{Linear-PRF construction. }
Here we consider a hash-based filter that was attacked by Neidermayer et al. in~\cite{xxx}.  Let $B_{\mathrm{lin}}=(\Hash,\Rep,\Qry)$ be defined as follows.  Fix non-empty sets~$\univ, \univ$ and integers $k,m>0$.  Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.  The $\Hash$ algorithm samples two keys $K_0,K_1 \getsr \mathcal{K}$ and defines $h_j(x) = F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$ for $j \in [k]$.  The $\Rep$ and $\Qry$ algorithms are the standard (determinisitic) BF ones. \tsnote{Should define these someplace.}  The following result shows, informally, that if~$F$ is a good PRF and the (non-adaptive) FP rate is sufficiently small, then $B_\mathrm{lin}$ is secure against adaptive FP-finding adversaries.

\begin{theorem}\label{thm1}
Fix $k,m,n>0$, and let $B_\mathrm{lin}=(\Hash,\Rep,\Qry)$ be the hash-based filter just described. 
Let~$A$ be an adversary, compatible with $\ExpFPSecHash{B_\mathrm{lin},t}{\cdot}$, that asks at most~$q$ queries to its $\QryOracle$ oracle.  Then there exist adversaries~$B_1$ and $B_2$ such that
\[
\AdvFPSecHash{B_{\mathrm{lin}},t}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + q \cdot  (1-e^{-kn/m})^k
\]
\end{theorem}
Before giving the proof, we note that  $(1-e^{-kn/m})^k \rightarrow 0$ as the ratio between the bit-length of the representation~$M$ and the size of the represented set~$S$, i.e.,$m/n$ tends to $\infty$.
\begin{proof}[Theorem~\ref{thm1}]
The proof of the theorem will use a game playing argument as shown in Fig. \ref{fig:Game}. $\game{0}(A)$ exactly simulates $\ExpFPSecHash{B,t}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$. So,
\begin{equation}
\AdvFPSecHash{B_{\mathrm{lin}},t}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
\end{equation}
 $\game{1}(A)$ and $\game{2}(A)$ attack 2 different filters with hash functions 
\begin{eqnarray*}
h_j(x) &=& ( F_{K_0}(x) + j\cdot \rho_2(x)) \bmod m\\
\mathrm{and,}\nudge h_j(x) &=& ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m 
\end{eqnarray*}

Here, $\rho_1$ and $\rho_2$ are random functions sampled from $Func(\univ,[m])$. Let adversaries $B_1, B_2$ simulate $\game{1}(A)$ and $\game{2}(A)$ respectively as shown in Fig. \ref{fig:BGame1}. When $b=1$, $B_1$ and $B_2$ exactly simulate $\game{0}(A)$
and $\game{1}(A)$. While, for $b=0$, $B_1$ wins, if $\game{1}(A)$ outputs 0, and  $B_2$ wins, if $\game{2}(A)$ returns 0.

@@

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.95}{
\hpagessd{.5}{.5}
{
\underline{\game{0}(A)}\\
$K_1, K_2 \getsr \calK$\\
$S \getsr \distr{\univ}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$K_1 \getsr \calK$\\
$\rho \getsr Func(\univ,[m])$\\
$S \getsr \distr{\univ}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = F_{K_1}(x)+i \cdot \rho(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{2}(A)}\\
$\rho_1,\rho_2 \getsr Func(\univ,[m])$\\
$S \getsr \distr{\univ}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{$\game{3}(A)$}\\
$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
$count = 0$ \\%count will be used to keep track of queries made to $\QryOracle$\\
$win \gets false$\\
$\rho_1,\rho_2 \getsr Func(\univ,[m])$\\
$S \getsr \distr{\univ}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
$count=count +1$\\
if $(count == \ell)$\\
$\nudge win = true$\\
$\nudge \mathrm{Ret} \nudge \Qry^{\HashOracle}(M,\tau,x)$\\
else \\
$\nudge \mathrm{Ret}\nudge 0$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\caption{Theorem \ref{thm1}:Game playing argument}\label{fig:Game}
\end{figure}

%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\begin{figure}
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\experimentv{Adversary \nudge B_1^{\calO}:}$\\
$K_1 \getsr \calK $\\
$S \getsr \distr{\univ}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
When $A$ halts with output $\calX^{'}$: \\
if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
}
{
$\experimentv{Adversary \nudge B_2^{\calO}:}$\\
%$d \getsr \bits $\\
$\rho_2 \getsr Func(\univ,[m])$\\
$S \getsr \distr{\univ}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
When $A$ halts with output $\calX^{'}$: \\
if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
%if $d=0$\\
$\mathrm{Ret} \nudge \calO(x) + i\cdot \rho_2(x)$, for $i\in[1,k]$
}
}
\caption{Theorem \ref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\end{figure}

@@

%\caption{Adversary $A^{'}$ simulating $\game{3}(A)$} \label{AGame3}
\begin{figure}
\centering
\fpage{0.4}{
$\experimentv{Adversary \nudge A^{{'}\HashOracle}:}$\\
$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
$count = 0$\\
$\rho_1,\rho_2 \getsr Func(\univ,[m])$\\
$S \getsr \distr{\univ}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge count = count + 1$\\
\nudge if $count == \ell$\\
$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,\tau,x)$\\
\nudge else\\
$\nudge$ $\nudge r = 0$\\
\nudge Ret $r$\\
When $A$ halts with output $\calX^{'}$\\
\nudge if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
\nudge\nudge Ret 0\\
\nudge if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
\caption{Theorem \ref{thm1}:Adversary $A^{'}$ simulating $\game{3}(A)$} \label{AGame3}
\end{figure}

### 2016-07-13 filters-syntax.tex
Updated Proof of Theorem 1 as per the changed syntax and some minor corrections
cleaning up theorem 1

\section{Hash-based Filters}
\heading{Preliminaries.}
When~$U$ is a set and $n>0$ is an integer, we let $[U]^n$ denote the set of all size-$n$ subsets of~$U$. We write $x \getsr U$ to denote sampling an element from~$U$ and assigning this to~$x$, and we extend this notation to randomized algorithms.

\heading{Syntax.}
Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$. An $(n,k,m)$-filter (over universe~$U$) is a tuple $B=(\Hash,\Rep,\Qry)$.
%
The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$ where each $h_i \in \mathrm{Func}(U,[m])$.  
\jnote{This doesn't seem to work super-well with the random oracle model.} 
\tsnote{Why not?  As we discussed on the phone, this should be fine.  In the ROM, if we ever need to simulate $\Hash$, we just do it by lazy sampling.}
We write $\mathcal{H} \getsr \Hash$ for this operation.
%
The randomized representation algorithm $\Rep\colon [U]^n \rightarrow \Sigma^m \times \bits^*$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$ along with (possibly empty) side-information~$\tau$.
%
The deterministic query algorithm $\Qry\colon \Sigma^m \times \bits^* \times U \rightarrow \bits$ takes a representation $M$, side-information~$\tau$, and an element $x \in U$, and returns a bit.
%
We assume that both $\Rep$ and $\Qry$ have blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$.  Typically this access will be implicit, but when we need to make it explicit we will write~$\mathcal{H}$ (or the individual hash functions) as superscripts.
%which we denote by writing~$\mathcal{H}$ as a superscript.
%Thus, we write $M \gets \Rep^{\mathcal{H}}(S)$ and $b \gets \Qry^{\mathcal{H}}(M,x)$ for the execution of the representation and query algorithms, respectively.
%
%We write $M \gets \Rep(S)$ and $b \gets \Qry(M,x)$ for the execution of the representation and query algorithms, respectively.
For correctness, we demand that for all~$S$ of size~$n$ and all $x \in S$, it holds that $\Prob{\mathcal{H}\getsr\Hash;\,(M,\tau)\getsr\Rep(S)\,:\,\Qry(M,\tau,x)=1}=1$, where the probability is over the coins of $\Hash$ and~$\Rep$.

>>>>

\section{Hash-based Filters}
\heading{Preliminaries.}
When~$\univ$ is a set and $n>0$ is an integer, we let $[\univ]^n$ denote the set of all size-$n$ subsets of~$\univ$. We write $x \getsr \univ$ to denote sampling an element from~$\univ$ and assigning this to~$x$, and we extend this notation to randomized algorithms.

\heading{Syntax.}
Fix nonempty sets $\univ,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in \univ$. An $(n,k,m)$-filter (over universe~$\univ$) is a tuple $B=(\Hash,\Rep,\Qry)$.
%
The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$ where each $h_i \in \mathrm{Func}(\univ,[m])$.  
\jnote{This doesn't seem to work super-well with the random oracle model.} 
\tsnote{Why not?  As we discussed on the phone, this should be fine.  In the ROM, if we ever need to simulate $\Hash$, we just do it by lazy sampling.}
We write $\mathcal{H} \getsr \Hash$ for this operation.
%
The randomized representation algorithm $\Rep\colon [\univ]^n \rightarrow \Sigma^m \times \bits^*$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$ along with (possibly empty) side-information~$\tau$.
%
The deterministic query algorithm $\Qry\colon \Sigma^m \times \bits^* \times \univ \rightarrow \bits$ takes a representation $M$, side-information~$\tau$, and an element $x \in \univ$, and returns a bit.
%
We assume that both $\Rep$ and $\Qry$ have blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$.  Typically this access will be implicit, but when we need to make it explicit we will write~$\mathcal{H}$ (or the individual hash functions) as superscripts.
%which we denote by writing~$\mathcal{H}$ as a superscript.
%Thus, we write $M \gets \Rep^{\mathcal{H}}(S)$ and $b \gets \Qry^{\mathcal{H}}(M,x)$ for the execution of the representation and query algorithms, respectively.
%
%We write $M \gets \Rep(S)$ and $b \gets \Qry(M,x)$ for the execution of the representation and query algorithms, respectively.
For correctness, we demand that for all~$S$ of size~$n$ and all $x \in S$, it holds that $\Prob{\mathcal{H}\getsr\Hash;\,(M,\tau)\getsr\Rep(S)\,:\,\Qry(M,\tau,x)=1}=1$, where the probability is over the coins of $\Hash$ and~$\Rep$.
